---
title: "Class Demo 9-2 11am"
author: "Wells"
date: "9/2/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Layout of Editor

1. Upper left: Text Editor

2. Lower left: Console

3. Upper Right: Environment

4. Lower Right: Files / Plots / Help 

Just typing. This isn't code.

1 + 2 


```{r}
1 + 2
```


## Coding Basic


create a vector

```{r}
v <- c(1, 4, 9, 16, 25)
```



operations on vectors

Take square root of every element of a vector

```{r}
sqrt(v)
```

```{r}
v + 1
```

A function applied to a vector applies the function to each element.

to update vector v (assign as the same name)

```{r}
v <- sqrt(v)
```



to undo, run the original function again:

```{r}
v <- c(1, 4, 9, 16, 25)
```

Usually good practice to give new names to new things:


```{r}
w <- sqrt(v)
```



Which elements of v are bigger than 10?


```{r}
v > 10
```


Other operations: greater than or equal to >=
Less than <
Less than or equal to <=
Equals == (two equal signs)
Not equals != 

Create new vector of elements of logicals for if elements of v are > 10.


```{r}
u <- v > 10
```

How many elements are greater than 10?

2, just by counting

Ask R:

```{r}
sum(u)
```


How do we write functions in R?


structure

```{r}
name_of_function <- function(variable1, variable6, pizza){
  variable1 + variable6*pizza
}
```

Recall the birthday problem. Suppose we have a group of k people and each chooses a number between 1 and n.

The probability of a match is

1 - n!/((n-k)!*n^k)

$$
1 - \frac{n!}{(n-k)! n^k} = 1 - \binom{n}{k}\frac{k!}{n^k}
$$

Write function to input n,k and return probability




```{r}
prob_bday_match <- function(n_bdays, k_people){
  1 - choose(n_bdays, k_people)*factorial(k_people)/(n_bdays^k_people)
}
```

How to plot in R (basic)?

To plot function of 1 variable:

1. need vector of inputs

2. need vector of corresponding outputs


Goal: Plot birthday probability for 25 students choosing from numbers between 50 and 25000.

View function at equally spaced points in domain

```{r}
n_bdays <- seq(from = 50, to = 1000, by = 25)
```


Evaluate function on n_bdays

```{r}
probs <- prob_bday_match(n_bdays, 25)
```

Use plot function applied to vectors of inputs and outputs


```{r}
plot(n_bdays, probs)
```






