---
title: "Loops in R"
author: "Wells"
date: "9/12/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


To perform a calculation or simulation several times, use the `replicate` function. Requires each trial to be independent and identical. 

But if formula in ith iteration depends on i, can't use replicate. Instead, use `for` *loops*

If we don't know at outset how many times to run experiment, we use `while` *loops*.

## Example For Loop

Suppose we want to add up first 20 integers.


```{r}
current_sum <- 0

for (i in 1:20){
  current_sum <- current_sum + i
  print( c(i, current_sum) )
}

```


## While Loops

Suppose we want to figure out how many times we need to multiply 2 by itself to exceed 1000


```{r}
my_product <- 1
steps <- 0

while (my_product <= 1000) {
  my_product <- my_product*2
  steps <- steps+1
  print(c(steps, my_product))
}


```

## Seven Before Nine

Suppose we roll a pair of dice repeatedly. What is the probability that a sum of 7 appears before a sum of 9?

```{r}
# to roll two dice and add
sum( sample(1:6, size = 2, replace = T) ) 
```

```{r}
seven_before_nine <- function(){
  my_sum <- 0
  steps <- 0
  
  while(my_sum != 7 & my_sum !=9){
    my_sum <- sum( sample(1:6, size = 2, replace = T) )
    steps <- steps+1
  }
  return(my_sum)
}
```


Now, run function 10,000 times

```{r}
n_times <- 10^4
sum( replicate(n_times, seven_before_nine()) == 7 ) / n_times
```



