---
title: "Demo 9-2 2pm"
author: "Wells"
date: "9/2/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Layout

4 panels:

1. Upper Left: Editor

2.Lower Left: Console

3. Upper Right: Environment

4. Lower Right: File / Plots / Packages


## The Editor

Components:

- The YAML (at the top)

- Regular text

- Code chunks


```{r}
1  + 2
```
1 + 2 

```{r}

```


Keyboard shortcut for new code chunk: 
- Option + CMD + I (mac)
- CTRL + ALT + I


## Coding Basics

To make a vector (from scratch)


```{r}
v <-  c(1, 4, 9, 16, 25)
```

Add 1 to every element in a vector


```{r}
v + 1
```

```{r}
sqrt(v)
```

Want to take square root of v and make that v
```{r}
v <- sqrt(v)
```

How to go back?


```{r}
v <-  c(1, 4, 9, 16, 25)
```

Call the square root vector w

```{r}
w <- sqrt(v)
```



Converting vectors of numbers to logicals


Which elements of v are > 10?


```{r}
v > 10
```

```{r}
u <- v > 10
```

Other logical operations on vectors:

1. Greater than or equal to: >=

2. Less than: <

3. Less than or equal to: <=

4. Equals: ==

5. Not equals: !=


How many entries of v are greater than 10?

In R, True is coded as 1 and False is coded as 0. 

Use sum function on a logical

```{r}
sum(u)
```

```{r}
sum(v > 10)
```


## Functions in R

Suppose we want to square every element of a vector and subtract 1.

write function f(x) = x^2 - 1.

```{r}
square_minus_one <- function(x){
  x^2 - 1
}
```

Functions of more than one variable:

f(x,y,z) = x*y - z

```{r}
new_function <- function(variable1, variable2, variable8)
{variable1*variable2 - variable8}
```

## Birthday Problem

Suppose we have k students selecting randomly from integers 1 through n.

The probability of at least 1 match is

1 - n!/((n-k)!n^k)

$$
1 - \frac{n!}{(n-k)!n^k} = 1 - \binom{n}{k} \frac{k!}{n^k}
$$
Define a function for birthday probability

```{r}
prob_bday_match <- function(n,k){
  1 - choose(n,k)*factorial(k)/n^k
}
```




## Quick Plotting in R

To make quick graphs, use plot



Plot requires:

1. A vector of inputs
2. A vector of outputs

To create a list of inputs, find equally spaced points in the domain.

Suppose we want birthday probs for 25 students for n between 50 and 1000, in multiples of 25 

```{r}
n <- seq(from = 50, to = 1000, by = 25)
```


create outputs

```{r}
probs <- prob_bday_match(n, 25)
```

To plot, apply plot function to vector of inputs and outputs


```{r}
plot(n,probs)
```



